---
title: "Vignette Title"
author:
  - "Name SURNAME"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---

```{r, pkgs, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(FLCore)
# LOAD other packages, including FLPKG, here
```

**FLPKG** is an open-source R package that imnplements/provides ... It makes use of the S4 classes and 
methods developed by the **FLR** project (<http://flr-project.org/R>, [@FLR_KellMG2007]), which simplify the development, testing and use of statistical and simulation models for fisheries management advice.
[...]
The package and documentation are available at <http://flr-project.org/FLPKG>.

# Introduction



# Background / Methods

This summation expression $\sum_{i=1}^n X_i$ appears inline.

This summation expression is in display form.

$$\sum_{i=1}^n X_i$$

# Using the FLPKG package

## Example / Workflow 1

## Example / Workflow 2

# More information

* You can submit bug reports, questions or suggestions on `FLPKG` at the `FLPKG` issue page ^[<https://github.com/flr/FLPKG/issues>], or on the *FLR* mailing list.
* Or send a pull request to <https://github.com/flr/FLPKG/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage ^[<http://flr-project.org>].
* The latest version of `FLPKG` can always be installed using the `devtools` package, by calling
```{r, devtools, echo=TRUE, eval=FALSE}
	library(devtools)
	install_github('flr/FLPKG')
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLPKG: `r # packageVersion('FLPKG')`
* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

## Author information

**Name SURNAME**. Affiliation. Address, Locality (RE) Country.

# References
