---
title: "Technical Manual for the *mse* FLR package"
author:
  - "Iago MOSQUEIRA, (EC JRC)"
  - "Ernesto JARDIM (EC JRC)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
tags: MSE FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---

```{r, pkgs, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(mse)
```

# Introduction

# The mse workflow



## Example / Workflow 1

## Example / Workflow 2

# S4 classes

## FLom

## FLmse

## FLoem

## FLiem

## mpCtrl

## mseCtrl

# Functions

## mp()

### goFish()

## performance()

## tunebisect()

# Extending mse with your own functions

## hcr

## sa

# More information

* You can submit bug reports, questions or suggestions on `FLPKG` at the `FLPKG` issue page ^[<https://github.com/flr/FLPKG/issues>], or on the *FLR* mailing list.
* Or send a pull request to <https://github.com/flr/FLPKG/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage ^[<http://flr-project.org>].
* The latest version of `FLPKG` can always be installed using the `devtools` package, by calling
```{r, devtools, echo=TRUE, eval=FALSE}
	library(devtools)
	install_github('flr/FLPKG')
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

## Author information

**Iago MOSQUEIRA**. European Commission Joint Research Centre. Ispra. Italy.
**Ernesto JARDIM**. European Commission Joint Research Centre. Ispra. Italy.

# References

